Asteroseismology: AI-Driven Seismic Event Detection for Extra-Terrestrial Missions\\

### 2025-05-25 paper.tex
check point final final

        CNNs are adept at automatically learning hierarchical features from data, making them suitable for analyzing raw
        seismic waveforms or their time-frequency representations (e.g., spectrograms) (Perol et al., 2018; Ross et al.,
        2018b). Generative Adversarial Networks (GANs) have also been explored, for instance, by Li et al. (2018) who
        used a GAN critic as an automatic feature extractor combined with a Random Forest classifier for discriminating
        earthquake P-waves from noise in early warning systems. This highlights the potential of ML to not only classify
        but also to learn compact and effective representations of seismic waves.

>>>>

        % CNNs are adept at automatically learning hierarchical features from data, making them suitable for analyzing raw
        % seismic waveforms or their time-frequency representations (e.g., spectrograms) (Perol et al., 2018; Ross et al.,
        % 2018b). Generative Adversarial Networks (GANs) have also been explored, for instance, by Li et al. (2018) who
        % used a GAN critic as an automatic feature extractor combined with a Random Forest classifier for discriminating
        % earthquake P-waves from noise in early warning systems. This highlights the potential of ML to not only classify
        % but also to learn compact and effective representations of seismic waves.
